Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-09-01 reanalysis-5-outcome_analysis.qmd
correct ses

@@

    # Calculate emmeans on the response scale
    emm <- emmeans(model, 
                   ~ ever_lapse_binary,
                   type = "response",
                   weights = "proportional")

>>>>

    # Get the data for this imputation (needed for emmeans)
    imp_data <- imputed_datasets[[i]]
    imp_data$weights <- twang_weights[[i]]

@@

    # Calculate emmeans on the response scale
    # Provide data explicitly for svyglm models
    emm <- emmeans(model, 
                   ~ ever_lapse_binary,
                   type = "response",
                   weights = "proportional",
                   data = imp_data)
